Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-11-28 inst/paper/main.tex
minor

The second substantial difference is the control that R gives over the
choice of environment in which the AST is evaluated in. Beside
traditional choices such as the top level or current lexical
environment, R allows programmers to choose a fresh, empty,
environment or any environment on the call stack. This is a
significant increase in expressive power as functions that are
otherwise not aware of the use of \eval may be deeply impacted.

>>>>

\medskip\noindent\textit{Environments.} In R, environments can be
manipulated at will. Each function has an environment that can be
accessed with \c{environment()}. A new environment, which by default
inherits from the current environment, is created with \c{new.env}.
Contrary to other values, environments have reference semantics rather
than copy semantics. The chain of inheriting environments can be
traversed with \c{parent.env}, ultimately one arrives at \c{emptyenv}.
\c{parent.frame} and \c{sys.frame} grant access to environments
further up in the calling stack, up to the global environment
\c{.GlobalEnv}, and packages. One can also directly read, modify or
create new bindings in any environments. Given an environment \c{e}:

\begin{itemize}
\item  \c{e$v} or \c{get("v", envir = e)} reads variable \c{v} in \c{e};
\item \c{e$v <- 2} or \c{assign("v", 2, envir = e)} writes value 2 in variable \c{v} in \c{e}. \c{v} is created if it did not exist in \c{e}.
\end{itemize}
\noindent One can directly modify a variable in the scope of its
calling function, and there is even a special assignment operator for
that purpose; \c{v <<- 2} will search for \c{v} in parent
environments, redefine the value, or create a definition in the
current environment. Environments are used as hashtables, to maintain
state across function calls, or to create package namespaces.
